Next Trippy Structures\thanks{Supported by organization x.}

### 2019-01-21 paper.tex
Update on Overleaf.
Copy previous refs

\section{Related works}
A nice review of all the R-Tree derivatives: \cite{john2017performance}.

@@

Finally, explain our work-in-progress model for trip representation, citing SPIRE. Newer models are largely irrelevant.

\subsection{Our previous works in trip representation}
So we speak about IS and SPIRE 2018 version here.

@@

\subsection{Common Structures}
Both \acumm and \ctr need a network representation to be operated, which is represented in the following components:

>>>>

\section{Related works}
Many data structures have been proposed to support efficient 
query capabilities on collections of
trajectories. We refer to~\cite[Chapter 4]{DBLP:books/sp/PelekisT14} for a comprehensive and
up-to-date survey on data management techniques for trajectories of moving objects. We can broadly
classify these data structures into two groups: those that index trajectories in free space and
those that index trajectories that are constrained to a network.

In free space, it is common to see spatial indexes that extend the {\em R-Tree} %spatial
index~\cite{DBLP:conf/sigmod/Guttman84} beyond a simple {\em 3D R-Tree} where the time is one of the dimensions.
Two examples of such indexes can be found in~\cite{DBLP:conf/vldb/PfoserJT00}
where the authors present two fundamental variations of the {\em R-Tree}: the {\em STR-Tree} and the {\em TB-Tree}.
Both indexes modify the classical construction algorithm for the {\em R-Tree},
where the nodes are not only grouped by the spatial distance among the indexed objects,
but also by the trajectories they belong to. In the {\em MV3R-tree}~\cite{DBLP:conf/vldb/PapadiasT01},
the construction takes into account temporal information of the moving objects,
adapting ideas from the Historical {\em R-Tree}~\cite{nascimento1998towards}. Another
interesting approach is described in~\cite{chakka2003indexing}, where the authors
split trajectories of moving objects across partitions of space, indexing each partition
separately. This improves query efficiency, as only the partitions that intersect
a query region are accessed.

{\em R-Tree} adaptations can also be useful when the trajectories are constrained to a network.
They exploit the constraints imposed by the topology of the network to optimize the data structure.
This is the case of the {\em FNR-tree}~\cite{DBLP:conf/ssd/Frentzos03}, which consists of a 
{\em 2D R-Tree} to index the %line 
segments of the trajectories over the network,
and a forest of {\em 1D R-Trees} used to index the time interval when each trajectory is moving through
each segment of the network.
The {\em MON-Tree}~\cite{DBLP:journals/geoinformatica/AlmeidaG05} can be seen as an
improvement over the {\em FNR-Tree}, saving considerable space by indexing MBRs of larger
network elements (edge segments or entire roads) and reducing the number of disk accesses at query time.
Both indexes are outperformed by the {\em TMN-Tree}~\cite{chang2010tmn} in query time,
which indexes whole trajectories of moving objects with a {\em 2D R$*$-Tree} and
indexing the temporal component with a B$⁺$-Tree, which proves to be more efficient for
that application than the {\em R-Tree}.
A nice review of all the R-Tree derivatives: \cite{john2017performance}.

{\em PARINET} is another interesting alternative to represent trajectories constrained to a network~\cite{DBLP:journals/vldb/PopaZOBV11}. %

It partitions trajectories into segments from an underlying road network using a
complex cost model to minimize the number of disk accesses at query time. It takes into
account the spatial relations among the indexed network elements, as well as some statistics
of the data to index. Then it adds a temporal B$⁺$-tree to index the trajectory segments from each road.
Those indexes permit {\em PARINET} to filter out candidate trajectory segments matching time constraints at query time.
The same ideas were used in {\em TRIFL}~\cite{that2015trifl}, where the cost model is adapted
for flash storage.

In another work~\cite{DBLP:conf/gis/KroghPTT14} the authors propose an indexing structure called {\em NETTRA} to answer  
{\em strict}  and {\em approximate path queries} that can be implemented in standard SQL using $B^+$-trees and self-JOIN operations.  
For each trajectory, {\em NETTRA} represents the sequence of adjacent network edges touched by the trajectory as  
entries in a table  with four columns:  id, entering and leaving time, and a hash value 
 of the entire path up to and including the edge itself.
Using the hash value  for the first and last
edge on a query path, {\em NETTRA}  determines whether
the trajectory followed a specific path between these edges.

@@

\subsection{Our previous works in trip representation}
So we speak about IS and SPIRE 2018 version here. Maybe stuff the brief explanation about WMs here too? Or move this and the next subsection to introduction.

@@

\subsection{Common Structures}
Both \acumm~and \ctr~need a network representation to be operated, which is represented in the following components:
